Nitrogen cycling in the CLM5: controls on responses to environmental forcing

### 2018-11-13 figures.tex

\begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_Br-cax_ens_MIC_y1_2012.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation at Caxiuan\~a National Forest}
     \label{CAX state}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US-Me2_ens_MIC_y1.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation at Metolius Forest State}
     \label{MET state}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US-NR1_ens_MIC_y1_2012.png}
     \caption{Niwot Forest State}
     \label{NR1 state}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US_Ha1_ens_MIC_y1_2012.png}
     \caption{Harvard Forest State}
     \label{HVF state}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US_Ha1_ens_MIC_p1_2012.png}
     \caption{Harvard Forest Nitrogen Fertilization}
     \label{HRV ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US_Ha1_ens_MIC_p1_2012.png}
     \caption{Harvard Forest CO2 Fertilization}
     \label{HRV celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_Br-cax_ens_MIC_p1_2012.png}
     \caption{Caxiuana Forest Nitrogen Fertilization}
     \label{CAX ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_Br-cax_ens_MIC_p1_2012.png}
     \caption{Caxiuana Forest CO2 Fertilization}
     \label{CAX celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth,left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p1_2012.png}
     \caption{Metolius Forest Nitrogen Fertilization}
     \label{MET ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-Me2_ens_MIC_p1_2012.png}
     \caption{Metolius Forest CO2 Fertilization}
     \label{MET celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US-NR1_ens_MIC_p1_2012.png}
     \caption{Niwot Forest Nitrogen Fertilization}
     \label{NR1 ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-NR1_ens_MIC_p1_2012.png}
     \caption{Niwot Forest CO2 Fertilization}
     \label{NR1 celev}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_GPP1__p2012.png}
     \caption{GPP CO2 and N respones}
     \label{GPP CO2 and N respones 2001}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_NPP1__p2012.png}
     \caption{NPP CO2 and N respones}
     \label{NPP CO2 and N respones 2001}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_TLAI1__p2012.png}
     \caption{LAI CO2 and N respones}
     \label{LAI CO2 and N respones 2001}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_TOTVEGC1__p2012.png}
     \caption{VEGC CO2 and N respones}
     \label{VEGC CO2 and N respones 2001}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_LEAFN1__p2012.png}
     \caption{Leaf Nitrogen CO2 and N respones}
     \label{Leaf N CO2 and N respones 2001}
  \end{figure}

>>>>

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US-NR1_ens_MIC_y1_2012.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation at Niwot Ridge.}
     \label{NR1 state}
 \end{figure}

  \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-NR1_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of CO$_{2}$ fertilization (550ppm) at Niwot Ridge}
     \label{NR1 celev}
  \end{figure}

  \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US-NR1_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of Nitrogen fertilization (+5 kgN m$^{2}$ y$^{-1}$) at Niwot Ridge}
     \label{NR1 ndep}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_GPP1__p2012.png}
     \caption{Influence of parameteric variation on the impact of 15 years of CO$_{2}$ and N fertilization on gross primary productivity (GPP), across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites. }
     \label{GPP CO2 and N respones 2001}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_NPP1__p2012.png}
     \caption{Influence of parametric variation on the impact of 15 years of CO$_{2}$ and N fertilization on net primary productivity (NPP), across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites.}
     \label{NPP CO2 and N respones 2001}
  \end{figure}

  \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_TLAI1__p2012.png}
     \caption{Influence of parametric variation on the impact of 15 years of CO$_{2}$ and N fertilization on leaf area index (LAI), across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites.}
     \label{LAI CO2 and N respones 2001}
  \end{figure}

  \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_TOTVEGC1__p2012.png}
     \caption{Influence of parametric variation on the impact of 15 years of CO$_{2}$ and N fertilization on vegetation carbon, across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites.}
     \label{VEGC CO2 and N respones 2001}
  \end{figure}

  \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_LEAFN1__p2012.png}
     \caption{Influence of parametric variation on the impact of 15 years of CO$_{2}$ and N fertilization on leaf nitrogen content ($N_{area}$), across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites.}
     \label{Leaf N CO2 and N respones 2001}
  \end{figure}
